Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
formatted table 2

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    % \toprule
    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    % \midrule
    % \multirow{2}{*}{FMNIST}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \midrule
    % \multirow{2}{*}{CIFAR-10}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \bottomrule
    % \end{tabular}
  \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$   \\
    \midrule
    \multirow{2}{*}{MNIST}
    & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
    & BNN predictive \cite{immer2021improving} & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003} \\
    & BNN predictive \cite{ritter2018kfac} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
    & GLM predictive \cite{immer2021improving} & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
    & GP predictive \cite{immer2021improving} $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
    & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
    & GP predictive $m=1024$  &  \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022} \\
    & \our NN $m=1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001} \\
    & \our $m=1024$ &  \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001} \\
    \midrule
    \multirow{2}{*}{FMNIST}
    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    & BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    & GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
    & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
    & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \bottomrule
  \end{tabular}

>>>>

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    % \toprule
    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    % \midrule
    % \multirow{2}{*}{FMNIST}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \midrule
    % \multirow{2}{*}{CIFAR-10}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \bottomrule
    % \end{tabular}
  \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
     Method & M &  & MNIST &  &  & FMNIST &  \\
            &   & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
    \midrule
    %\multirow{2}{*}{MNIST}
    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
          & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
                                               & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
                                           & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\

    GP predictive NN & $1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
                              &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\

    GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
                            & \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
                     &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
                  & \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \midrule
%    \multirow{2}{*}{FMNIST}
%    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    %& BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    % & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    % & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    %& GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
    % & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
    % & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    % & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \bottomrule
  \end{tabular}
